Deciding to Disclose: Pregnancy and Alcohol Misuse

### 2014-07-07 Background.tex
Making the sections, slowly
Added tex  root for easier building
Sketching out
Fleshing out
Beginning to flesh out, added a stub for a decision problem figure.

\section{Background}

\label{ch:lit_review}

This chapter presents an overview of literature focusing on the impact
of drinking behaviour in pregnancy, and factors affecting disclosure
behaviour in the midwifery context. This is followed by a review of
literature supporting the theoretical underpinning of the modelling
approach, with particular reference to statistical decision theory.

\subsection{Alcohol, and Disclosure in the Maternity Setting}

@@

\subsection{Games, Signals, and Decisions}

@@

Bayesian decision theory, as expounded by \citet{Robbins1964} applies
Bayesian inference to the process of decision making under some degree
of uncertainty, on the basis that the decision is a repeated one.
The central idea is relatively straightforward, and assumes that the
loss or gain of some action to resolve a decision is contingent on
an unknown parameter. To solve the problem, the decision maker chooses
whichever action will minimise the risk, where the risk of an action
is $\underset{i}{\sum}\lambda(a_{j}|w_{i})P(w_{i}|x)$, i.e. the loss
incurred for taking action $a_{j}$ given that the true state of the
world is $w_{i}$, multiplied by the belief that this is the true
state of world given evidence $x$, summed across all possible worlds.
Essentially this is identical with expected value, with Bayesian style
probabilities. This allows an additional process of inference to progressively
update the distribution from which $P(w_{i}|x)$ derives, as new evidence
is obtained after each decision.

>>>>

%!TEX root = disclosure_game.tex
\section{Background}

\label{sec:lit_review}

This section presents a brief overview of literature focusing on the impact
of drinking behaviour in pregnancy, and factors affecting disclosure
behaviour in the midwifery context. This is followed by a review of
literature supporting the theoretical underpinning of the modelling
approach, with particular reference to statistical decision theory.

\subsection{Alcohol, and Disclosure in the Maternity Setting}
\label{sub:alcohol_disclosure}

@@

\subsection{Games, Signals, and Decisions}
\label{sub:games_signals}

@@

Bayesian decision theory, as expounded by \citet{Robbins1964} applies
Bayesian inference to the process of decision making under some degree
of uncertainty, where decisions may be one-shot, or repeated.
The central idea is relatively straightforward, and assumes that the
loss or gain of some action to resolve a decision is contingent on
an unknown parameter. To solve the problem, the decision maker chooses
whichever action will minimise the risk, where the risk of an action
is $\underset{i}{\sum}\lambda(a_{j}|w_{i})P(w_{i}|x)$, i.e. the loss
incurred for taking action $a_{j}$ given that the true state of the
world is $w_{i}$, multiplied by the belief that this is the true
state of world given evidence $x$, summed across all possible worlds.
Essentially this is identical with expected value, with Bayesian style
probabilities. This allows an additional process of inference to progressively
update the distribution from which $P(w_{i}|x)$ derives, as new evidence
is obtained after each decision.

### 2014-07-07 Introduction.tex
Fleshing out
Beginning to flesh out, added a stub for a decision problem figure.

The remainder of this paper proceeds to provide small reviews of alcohol and disclosure in the maternity setting (\ref{sub:alcohol_disclosure}), and the methodological context (\ref{sub:games_signals}), before outlining the model (\ref{sec:model}), and experiments (\ref{sec:method}), with selected results (\ref{sec:results}), then closing with a discussion contrasting the decision models (\ref{sec:conclusion}).

>>>>

The remainder of this paper proceeds to provide brief reviews of alcohol and disclosure in the maternity setting (\ref{sub:alcohol_disclosure}), and the methodological context (\ref{sub:games_signals}), before outlining the model (\ref{sec:model}), and experiments (\ref{sec:method}), with selected results (\ref{sec:results}), then closing with a discussion contrasting the decision models (\ref{sec:conclusion}).

### 2014-07-07 Methods.tex
Added tex  root for easier building
Fleshing out
Beginning to flesh out, added a stub for a decision problem figure.

\section{Method}
\label{sec:method}
%Lay out the design of experiments, harking back to things we're looking for
%from the real world.
%explicit subsection on the SA.
\subsection{Global Sensitivity Analysis}
\label{sub:sensitivity}

>>>>

%!TEX root = disclosure_game.tex
\section{Method}
\label{sec:method}
%Lay out the design of experiments, harking back to things we're looking for
%from the real world.

This section provides details of experiments conducted to examine the ability of the model to reproduce qualitative trends reported in the midwifery literature by \cite{Alvik2006}, and \cite{Phillips2007}; as well as a global sensitivity analysis and construction of statistical emulators to explore, and contrast the response surfaces of the four decision rules.

\subsection{Qualitative Trends}
\label{sub:qt}
%explicit subsection on the SA.

Throughout this paper, parameters for the \ac{CPT} model were as used in \cite{Tversky1992} (table \ref{tab:qt_params}). While there has been significant work on determining appropriate parameterisation for the model (e.g. \cite{Neilson2002}, \cite{Glockner2012}, \cite{Nilsson2011}), a full exploration of the impact of these parameters, or heterogeneous values within populations is beyond the scope of this work.

Two key measures were used - the fraction of the subpopulation who had ever signalled honestly, and the proportion referred. Both measures were taken after every round of play, and were taken relative to the agent's position in their sequence of appointments giving the probability of signalling honestly, or being referred having had a given number of appointments.

\begin{table}
\center
\begin{tabular} {l | c}
Name & Value \\

\end{tabular}
\caption[Table caption text]{Model parameters. \label{tab:qt_params}}
\end{table}
\subsection{Global Sensitivity Analysis}
\label{sub:sensitivity}
%Maxmin latin hypercube -> remember to cite the r package used.
%Will require some discussion of the gemsa technique at this point - can also cite Jason H for precedent!
 \cite{Bijak2013b}

Parameters for training were generated in R \citep{RTeam2014} using Latin Hypercube Sampling \citep{Carnell2012} over the space of inputs given in table \ref{tab:sa_params}. Initially a unit hypercube was generated, then the margins transformed appropriately to cover those regions where the inputs are not bounded between 0 and 1, and for proportions of agent types which necessarily sum to one across the three parameters. Given the limitation of 400 design points for the \ac{GEM-SA} software, we produced exactly that many parameter combinations and collected results for 100 runs of each. A fixed set of 100 random seeds was used, such that each parameter set was run once with each seed, for every decision rule.

To better capture the response characteristics for the model, we employ three - (1) the interquartile range of the average signal sent by each type of agent in a run, (2) the average signal of moderate drinking agents in a run, and (3) the standard deviation of that average signal between simulation runs. Together these three metrics give an indication of how far women are separable by their signalling behaviour (1), the behaviour of the at risk drinking groups\footnote{Under most conditions, the behaviour of heavy drinkers tracks closely with their moderate counterparts.} (2), and finally the stability of the system in the face of the stochastic elements.

Measurements were taken at the end of 1000 rounds of play, and for 1 and 2, 400 results were selected covering the full hypercube with each chosen randomly from the runs for that design point. This approach, rather than averaging across runs, was taken to avoid obscuring the high degree of variability evident in the output of the payoff reasoning agents in some areas of the parameter space.

Twelve emulators were built, covering each of the three output on all four decision models. These emulators were used to conduct a probabalistic sensitivity analysis using \ac{GEM-SA} to assess the impact of parameters individually, and in combination. In addition, the trained emulators were used to explore novel areas of the parameter space.?????????????

\begin{table}
\center
\begin{tabular} {l | c}
Name & Value \\

\end{tabular}
\caption[Table caption text]{Parameter ranges. \label{tab:sa_params}}
\end{table}

\begin{table}
\center
\begin{tabular} {l | c}
Name & Value \\

\end{tabular}
\caption[Table caption text]{Output measures. \label{tab:sa_measures}}
\end{table}

### 2014-07-07 Model.tex
Fleshing out
Beginning to flesh out, added a stub for a decision problem figure.

@@

Midwives are treated in a similar fashion, where their type corresponds to how negatively they regard a drinking pattern - non-judgemental, moderately judgemental, and harshly judgemental. The expression of this judgement is not a matter of choice on their part, and is assumed not to impact on their choice of response, which is either to refer the woman for specialist treatment, or to do nothing.

@@

Agents treat this two player game as taking place against nature, along the lines of adversial risk analysis \citep{THINGY}.

@@

While in principle a wide variety of agent models, given that decision rules operate on essentially the same information, and produce the same outputs, we limit ourselves here to four. The simplest is a lexicographic rule (1), motivated as in the spirit of a \ac{FFH} \citep{Gigerenzer2004} which uses only information about payoffs given actions; a Bayesian risk minimisation rule using the same information (2); a second Bayesian risk rule (3) which uses information about the underlying lottery; and a two-stage \ac{CPT} \cite{Hau2008} agent (4) which is identical with 3, but uses the \ac{CPT} decision rule from \cite{Tversky1992}.

@@

@@

@@

It would seem unreasonable to suppose that neither party recounts their experiences to their peers, and to explore the impact of this we also modify the game to introduce a simple form of information sharing within agent groups. This takes the form of having each agent share their memories with their colleagues with some probability \(p\). Individuals then incorporate shared information into their beliefs using weighted updates, such that a shared observation of a low type signal contributes to their beliefs by \(q\), and \(0\leq q\leq 1\). Women share only when they have finished play, and provide their complete history of games, because they have accurate information about the outcomes. By the same rationale, midwives share only their history with the most recent woman they referred. Sharing occurs simultaneously for all players at the end of each round, and all memories are either shared immediately or discarded.\footnote{Memories of games remain, but the assumption is that only current news is relevant.}

@@

By contrast, representing the problem in terms of the probabilities of the individual lotteries yields a structure that generalises the new information.

>>>>

In this section we outline the disclosure game model, and give details of the four decision rules.

A brief sketch of a pregnancy in terms of encounters between a woman and a midwife is instructive at this juncture. Typically women will have 12 appointments with a midwife during the antenatal period. Outside of caseloading teams, a woman does not generally have a named midwife, and may see a different practitioner at each appointment. In the UK, and unlike most healthcare scenarios, maternity notes are patient held, so midwives do not have extensive information prior to an appointment unless they have encountered the woman previously. Maternity notes are not generally linked to extra-departmental records, meaning that a history of alcohol related admissions to another service may remain unknown unless revealed by the woman.

According to NICE guidance \citep{NICE2010a,NICE2010} substance misuse should be raised at the initial booking appointment, and subsequent action if a concern is raised is at the discretion of the midwife. This may take the form of specific guidance to reduce intake, or if deemed necessary a referral to a specialist midwife and relevant interdisciplinary team. On alcohol consumption, policy regarding how to determine the level of consumption is generally at the trust level, or according to the best judgement of the individual midwife, with no guidance provided by NICE. This commonly takes the form of average units per week, but may include \ac{T-ACE} and similar measures.

Beyond the booking appointment, the onus is on women to raise concerns about their drinking behaviour, or the midwife to probe further if they feel it is warranted.

@@

Midwives are treated in a similar fashion, where their type corresponds to how negatively they regard a drinking pattern - non-judgemental, moderately judgemental, and harshly judgemental. The expression of this judgement is not a matter of choice on their part, and is assumed to have no impact on their response, which is to either refer the woman for specialist treatment, or do nothing.

@@

Taken together, this leads to a game tree that is relatively complex even at the subgame level (figure \ref{fig:subgame_tree} shows the subgame tree, with information sets). 
%The subgame has a large number of pure Nash equilibria, and solution using Gambit \citep{Gambit13}
Rather than attempt to solve for equilibria, agents treat this two player game as taking place against nature, along the lines of adversial risk analysis \citep{RiosInsua2009}. This effectively translates the game to a pair of decision problems, which agents attempt to resolve at each turn using a simple decision rule.

@@

While in principle a wide variety of agent models are possible, given that decision rules operate on essentially the same information, and produce the same outputs, we limit ourselves here to four. The simplest is a lexicographic rule (1), motivated as in the spirit of a \ac{FFH} \citep{Gigerenzer2004} which uses only information about payoffs given actions; a Bayesian risk minimisation rule using the same information (2); a second Bayesian risk rule (3) which uses information about the underlying lottery; and a two-stage \ac{CPT} \cite{Hau2008} agent (4) which is identical with 3, but uses the \ac{CPT} decision rule from \cite{Tversky1992}. Hence, each successive decision model adds a layer of sophistication to the problem representation while retaining the same input-ouput characteristics.

@@

A simplifying assumption is made that all midwives have just qualified, with identical training and as a result have entirely homogenous beliefs about their women. It is assumed in general that they have not been trained by Dr. House, and as a result have been taught that people will generally tell the truth.
Women are heterogenous in their prior observations, which are assigned stochastically and constrained such that they have encountered each scenario possible at least once, with exactly \(k\) encounters overall.

@@

The most complex decision rule used is \ac{CPT}, which attempts to reproduce a number of systematic deviations from rationality observed in humans. While \ac{CPT} has primarily been applied in the context of decisions from description, it has been modified to deal with decisions from experience by incorporating a first stage where probabilities are estimates from observations as in \cite{Hau2008}. In this instance we replace the frequentist first stage with the equivalent Bayesian inference process.

@@

It would seem unreasonable to suppose that neither party recounts their experiences to their peers, and to explore the impact of this we also modify the game to introduce a simple form of information sharing within agent groups. This takes the form of having each agent share their memories with their colleagues with some probability \(p\). Individuals then incorporate shared information into their beliefs using weighted updates, such that a shared observation of a low type signal contributes to their beliefs by \(q\), and \(0\leq q\leq 1\). Women share only when they have finished play, and provide their complete history of games, because they have accurate information about the outcomes. By the same rationale, midwives share only their history with the most recent woman they referred. Sharing occurs simultaneously for all players at the end of each round, and all memories are either shared immediately or discarded.\footnote{Memories of games remain, but it is assumed that only current news is relevant.}

@@

By contrast, representing the problem in terms of the probabilities of the individual lotteries yields a structure that abstracts the new information from payoffs, and allows the agent discount implausible outcomes.
